---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dev = "ragg_png",
  dpi = 300
)
```

# mitchhenderson

<!-- badges: start -->

<!-- badges: end -->

This is a package to store useful helper functions for personal use such as `ggplot2` and `gt` themes, and social media captions.

## Installation

You can install the development version of mitchhenderson from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mitchhenderson/mitchhenderson")
```

## Social captions

The `social_caption()` function generates a HTML string that, when rendered, shows LinkedIn, Bluesky, and GitHub usernames and icons.

```{r example}
library(mitchhenderson)

socials <- social_caption(icon_colour = "dodgerblue", 
                          font_colour = "black")

socials
```

This can be used as a caption on ggplot objects.

```{r plot, echo = FALSE}
library(ggplot2)
library(ggtext)


df <- data.frame(x = 0:10, y = 0:10)

df |>
  ggplot(aes(x, y)) +
    labs(caption = socials) +
    theme(plot.caption = element_markdown())
```

## New post

The `new_post()` function will create a new folder and `.qmd` file in the posts folder of my website project. The arguments to the function will pre-fill the YAML. This function was found on [Thomas Mock's blog](https://themockup.blog/posts/2022-11-08-use-r-to-generate-a-quarto-blogpost/) with only a very minor modification to remove the console interactivity.

```{r new post, eval=FALSE}
new_post(
   title = "My new post",
   description = "My new post is about xyz",
   draft = TRUE
)
```
