---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dev = "ragg_png",
  dpi = 300
)
```

# mitchhenderson

Helper functions I use across my own projects, mostly for the charts and posts on [mitchhenderson.dev](https://mitchhenderson.dev). It's built for me, so the defaults are my name and my fonts, but you're welcome to use it or copy from it.

## Installation

``` r
# install.packages("remotes")
remotes::install_github("mitchhenderson/mitchhenderson-R-package")
```

## Social captions

`social_caption()` returns an HTML string with LinkedIn, Bluesky and GitHub icons and usernames. The icons need the Font Awesome 7 Brands font installed.

```{r example}
library(mitchhenderson)

socials <- social_caption(icon_colour = "dodgerblue",
                          font_colour = "black")

socials
```

Use it as a plot caption, with `ggtext::element_markdown()` to render the HTML.

```{r plot, fig.height = 3.5}
library(ggplot2)
library(ggtext)

ggplot(mtcars, aes(wt, mpg)) +
  geom_point() +
  labs(caption = socials) +
  theme(plot.caption = element_markdown())
```

## New post

`new_post()` creates a folder and `.qmd` file in the `posts/` folder of a Quarto site, with the YAML filled in from the arguments. It's from [Thomas Mock's blog](https://themockup.blog/posts/2022-11-08-use-r-to-generate-a-quarto-blogpost/), with a small change to remove the console prompts.

```{r new post, eval=FALSE}
new_post(
   title = "My new post",
   description = "My new post is about xyz",
   draft = TRUE
)
```
